Improve SSD with Feature Fusion, \\IoU Loss and Super Resolution

### 2019-12-29 report/paper.tex
add some figures to the report

\usepackage{fontspec}
% \usepackage{cite}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  In the AI course project, we mainly follow the one-stage detector design, and we show it is possible to achieve both better efficiency and higher accuracy with optimized network architectures, refined losses and super-resolution inputs.
\end{abstract}

@@

\subsection{Feature Fusion}
One of the main difficulties in object detection is to effectively represent and process multi-scale features. Earlier detectors often directly perform predictions based on the pyramidal feature hierarchy extracted from backbone networks \cite{caiunified, liussd, sermanetoverfeat} . As one of the pioneering works, feature pyramid network (FPN)~\cite{linfeature2} proposes a top-down pathway to combine multi-scale features. Following this idea, PANet~\cite{liupath} adds an extra bottom-up path aggregation network on top of FPN; STDL~\cite{zhouscale} proposes a scale-transfer module to exploit cross-scale features, and G-FRNet~\cite{amirulgated} introduces gate units for controlling information flow across features. More recently, NAS-FPN~\cite{ghiasifpn} leverages neural architecture search to automatically design feature network topology. We use our BiFPN layer to optimize multi-scale feature fusion with a more intuitive and principled way.

@@

\subsection{Network Structure Overview}
The whole SSD network can be organized into three parts

@@

To address the issue of one-way flow information limitation, our BiFPN layer adds an extra bottom-up path aggregation network, which idea is inspired by PANet. The idea of PANet is shown in Figure~ref{fig:bifpn}.

@@

>>>>

\usepackage{fontspec}
\usepackage{multirow}
% \usepackage{cite}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  In this project, we mainly follow the one-stage detector design, and propose some methods to improve SSD for better small object detection performance. We show that it is possible to achieve both better efficiency and higher accuracy with refined network architectures, BiFPN feature fusion, additional IoU losses and super-resolution inputs.
\end{abstract}

@@

\subsection{Feature Fusion}
One of the main difficulties in object detection is to effectively represent and process multi-scale features. Earlier detectors often directly perform predictions based on the pyramidal feature hierarchy extracted from backbone networks \cite{caiunified, liussd, sermanetoverfeat} . As one of the pioneering works, feature pyramid network (FPN)~\cite{linfeaturee} proposes a top-down pathway to combine multi-scale features. Following this idea, PANet~\cite{liupath} adds an extra bottom-up path aggregation network on top of FPN; STDL~\cite{zhouscale} proposes a scale-transfer module to exploit cross-scale features, and G-FRNet~\cite{amirulgated} introduces gate units for controlling information flow across features. More recently, NAS-FPN~\cite{ghiasifpn} leverages neural architecture search to automatically design feature network topology. We use our BiFPN layer to optimize multi-scale feature fusion with a more intuitive and principled way.

\begin{figure*}[htbp]
  \centering
  \includegraphics[width=\linewidth]{fig/ssd.PNG}
  \caption{Original SSD structure}\label{fig:ssd}
\end{figure*}

@@

\subsection{Network Structure Overview}
The whole SSD network can be organized into three parts, which is shown in Figure~\ref{fig:ssd}.

@@

To address the issue of one-way flow information limitation, our BiFPN layer adds an extra bottom-up path aggregation network, which idea is inspired by PANet. The idea of PANet is shown in Figure~\ref{fig:bifpn}.

@@

The training process is shown in Figure~\ref{fig:train}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{fig/all.png}
  \caption{The training process}\label{fig:train}
\end{figure}
